Community Data Science meets Digital Heritage: Controversies about World Heritage Sites in the Online Community of Wikipedia

### 2019-03-29 code/paper.Rmd
time series!

revision_history_page_details_ip_addresses <- 
randoms_revision_history_page_details %>% 
  mutate()
  mutate(edits_from_ip_addresses = map(revision_history_page_details,
                          ~.x %>% 
                            filter(get_ip_addresses(rh_user) != "") %>% 
                            mutate(ip_location = map(rh_user, 
                                                     ~maxmind(.x, ip_db)))  %>% 
                            unnest(ip_location)))

@@

>>>>

@@

time series of edits: breakouts relating to events? monthly seems like a good level of aggregation. What can we do for spike detection?

```{r}
randoms_revision_history_page_details_ip_location %>% 
  group_by(page) %>% 
  mutate(the_d = floor_date(rh_date, "day")) %>% 
    mutate(the_m = floor_date(rh_date, "month")) %>% 
  group_by(page, the_m) %>% 
  tally() %>% 
  filter(n() > 130) %>%   # explore this value
  ggplot() +
  geom_line(aes(the_m,
             n)) +
  facet_wrap( ~ page, scales = "free")
```
